Demography and selection since maize domestication

### 2015-06-08 manuscript.tex
new figs

\begin{figure*}[b]
%\vspace*{.05in}
\centering
\includegraphics[width=.45\textwidth]{FigsAndFiles/plotDiversity_TvM_Folded2_unNeutralized_June} \includegraphics[width=.45\textwidth]{FigsAndFiles/plotDiversity_TvT_Folded2_unNeutralized_June}
\caption{Pairwise diversity surrounding synonymous and nonsynonymous
  substitutions in maize and teosinte. A: Maize diversity; B: Teosinte
diversity.}
\label{hardSweeps}
\end{figure*}

>>>>

\begin{figure*}[b]
%\vspace*{.05in}
\centering
\includegraphics[width=.45\textwidth]{FigsAndFiles/plotDiversity_TvM_Folded2_Significance_June}
\hspace{0.05\textwidth} \includegraphics[width=.45\textwidth]{FigsAndFiles/plotDiversity_TvT_Folded2_Significance_June}
\caption{Pairwise diversity surrounding synonymous and nonsynonymous
  substitutions in maize and teosinte. A: Maize diversity; B: Teosinte
diversity.}
\label{hardSweeps}
\end{figure*}
